\vspace{-0.25em}\thetitle

### 2009-07-28 paper.tex
...

@@

% real-world network traces tend to have approximately low-rank representation matrices despite the potential rank of such matrices being very large.
% Moreover, most flows' vectors lie on only one of a few even lower rank subspaces.
% Moreover, the low-rank subspace near which real traffic lies can be decomposed into subspaces of even lower rank, with almost all flows lying in one of these subspaces.
% Typically, these smaller subspaces are one-dimensional, but in some cases they may have up to a dozen dimensions.

% the vast majority of observed flow behaviors in any given trace lie in one of a handful low-rank subspaces.
% These subspaces are mostly of rank one, but a few have dimensions as high as ten.

% Karpinski~\emph{et~al.}~\cite{Karpinski08} further observed that the simplifications commonly used in traffic modeling correspond to multiplication of traffic representation matrices by low-rank matrices, averaging over rows or columns.
% They demonstrated experimentally that such simplifications severely distort important behavioral properties of traffic traces;
% viewing these simplification as low-rank matrix transformations, this is unsurprising:
% most of the detail of the original traffic behavior is destroyed.
% It was suggested that matrix factorization provides an alternative and superior means of model reduction.

@@

\section{Model \& Hypothesis}\sec{model-hypothesis}

@@

Our experimental methodology has three parts:
training, prediction and evaluation.
For training, we take a sample of network trace traffic and try to recover the structure hypothesized in \Section{model-hypothesis} from it.
For prediction, we use the trained model to predict behaviors of a separate set of flows from the same trace, using only knowledge of a few initial packets of each.
Finally, we must evaluate the quality of these predictions.
As noted in the \Section{introduction}, due to nondeterminism we cannot possibly predict exact behaviors of flows and must instead evaluate how good a predicted distribution of possible behaviors is as compared to actual outcomes.
% One relatively intuitive measure of prediction quality we use is threshold testing.

@@

>>>>

The rest of this paper is organized as follows.
In \Section{background}, we provide some background and the present the observations which motivate this work.
Our model and hypothesis about flow behavior is presented in \Section{hypothesis}.
The experimental methodology for testing this hypothesis is presented in \Section{methodology}, and the results follow in \Section{results}.
\Section{discussion} discusses the meaning and impact of our results.
\Section{related-work} gives context for this work in relation other research.
We conclude with final remarks in \Section{conclusions}.

@@

@@

\section{Model \& Hypothesis}\sec{model}\sec{hypothesis}

@@

Our experimental methodology has three parts:
training, prediction and evaluation.
For training, we take a sample of network trace traffic and try to recover the structure hypothesized in \Section{hypothesis} from it.
For prediction, we use the trained model to predict behaviors of a separate set of flows from the same trace, using only knowledge of a few initial packets of each.
Finally, we must evaluate the quality of these predictions.
As noted in the \Section{introduction}, due to nondeterminism we cannot possibly predict exact behaviors of flows and must instead evaluate how good a predicted distribution of possible behaviors is as compared to actual outcomes.
% One relatively intuitive measure of prediction quality we use is threshold testing.

@@

\section{Related Work}\sec{related-work}
